 

### 2023-05-15 appendix_2.2.Rmd
Additional typesettting changes

# data_mh_dup_names %>%
#   dplyr::select(region, clinic_name) %>%
#   unique() %>%
#   filter(clinic_name %in% duplicates) %>%
#   relocate(clinic_name, .before = region) %>%
#   arrange(clinic_name) %>%
#   group_by(clinic_name) %>%
#   summarise(region = paste(region, collapse = " | ")) %>%
#   unique() %>%
#   rename("Facility name" = clinic_name,
#          "Regions" = region) %>%
#   gt() %>% 
#   tab_header(
#     title = md("**Examples of duplicate facility names in different regions**")) %>%
#   tab_options(table.font.names = "Source Sans Pro") %>%
#   tab_style(
#     locations = cells_column_labels(),
#     style     = list(
#       cell_text(weight = "bold"))
#   )

@@

``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique()
column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique()

r_old <- column1 %>% dplyr::select(region_name) %>% unique()
r_new <- column2 %>% dplyr::select(region) %>% unique()

cbind(r_old, r_new) %>% mutate(test = region_name == region) %>%
  filter(test == FALSE) %>%
  relocate(region, .before = region_name) %>%
  rename("Name in data" = region,
         "Standardized name" = region_name) %>%
  dplyr::select(!test) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.6: Standardization of region names**"))

@@

``` {r table_standardization_district_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika")

district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika")

as.data.frame(cbind(district_old, district_new)) %>%
  arrange(district_old) %>%
  rename("Name in data" = district_old,
         "Standardized name" = district_new) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.7: Standardization of district names**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )
```

@@

``` {r table_standardization_district_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I")

district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno")

district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato")

as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>%
  arrange(district_tobechanged) %>%
  relocate(district_communes_affected, .before = district_tobechanged) %>%
  rename("District name in data" = district_tobechanged,
         "Communes" = district_communes_affected,
         "District name, updated" = district_changed) %>%
  gt() %>% 
  tab_header(
    title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )

```
\addcontentsline{lot}{table}{Table S2.9: Standardization of commune names.}

``` {r table_standardization_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord",
                 "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana", 
                 "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho",
                 "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary",
                 "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud",
                 "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy",
                 "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao",
                 "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso",
                 "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona",
                 "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina",
                 "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika",
                 "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy",
                 "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord",
                 "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe",
                 "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I",
                 "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda",
                 "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe",
                 "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut",
                 "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity",
                 "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba",
                 "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka",
                 "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)",
                 "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo", 
                 "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare", 
                 "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II",
                 "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain",
                 "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud",
                 "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat",
                 "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra",
                 "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka")

commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord",
                 "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava", 
                 "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana",
                 "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud",
                 "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka",
                 "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo",
                 "Ampasimboraka", "Ampasimpotsy Sud", "Ampasimpotsy Gara", "Ampasipotsy Mandialaza", "Manampaneva", "Ampatakamaroreny", "Anakao", "Analaiva", "Analamisampy",
                 "Analamitsivalana", "Ambatomainty", "Antanandava", "Andrainjato Est", "Andimaky Manambolo", "Andoharanomaitso", "Andoharanomaitso", "Andrainjato Centre",
                 "Andranohinaly", "Andranomiditra", "Rambolamasoandro Andranomiely", "Andranovorivato", "Andranovory", "Andravola Vohipeno", "Andrebakely Nord", "Andribavontsona",
                 "Androndrono", "Androy", "Anjampaly", "Anjeky Ankilikira", "Anjeva Gara", "Anjiabe Ambony", "Anjiajia", "Anjoman'ankona", "Anjoma Itsara", "Ankadinondry Sakay",
                 "Ankafina Tsarafidy", "Ankarinarivo Manirisoa", "Ankaromalaza Mifanasoa", "Ankasakasa Tsibiray", "Ankazoabo Sud", "Ankazotokana", "Ankiabe-Salohy", " Ankiakabe Nord",

>>>>

# data_mh_dup_names %>%
#   dplyr::select(region, clinic_name) %>%
#   unique() %>%
#   filter(clinic_name %in% duplicates) %>%
#   relocate(clinic_name, .before = region) %>%
#   arrange(clinic_name) %>%
#   group_by(clinic_name) %>%
#   summarise(region = paste(region, collapse = " | ")) %>%
#   unique() %>%
#   rename("Facility name" = clinic_name,
#          "Regions" = region) %>%
#   gt() %>% 
#   tab_header(
#     title = md("**Examples of duplicate facility names in different regions**")) %>%
#   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
#   tab_style(
#     locations = cells_column_labels(),
#     style     = list(
#       cell_text(weight = "bold"))
#   )

@@

```{r table_s_2_6, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_2_6.png")

<!-- ``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique() -->
<!-- column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique() -->

<!-- r_old <- column1 %>% dplyr::select(region_name) %>% unique() -->
<!-- r_new <- column2 %>% dplyr::select(region) %>% unique() -->

<!-- cbind(r_old, r_new) %>% mutate(test = region_name == region) %>% -->
<!--   filter(test == FALSE) %>% -->
<!--   relocate(region, .before = region_name) %>% -->
<!--   rename("Name in data" = region, -->
<!--          "Standardized name" = region_name) %>% -->
<!--   dplyr::select(!test) %>% -->
<!--   gt() %>% -->
<!--   tab_header( -->
<!--     title = md("**Table S2.6: Standardization of region names**")) %>% -->
<!--   gtsave("table_s_2_6.docx") -->

@@

```{r table_s_2_7, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_2_7.png")

<!-- ``` {r table_standardization_district_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika") -->

<!-- district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika") -->

<!-- as.data.frame(cbind(district_old, district_new)) %>% -->
<!--   arrange(district_old) %>% -->
<!--   rename("Name in data" = district_old, -->
<!--          "Standardized name" = district_new) %>% -->
<!--   gt() %>% -->
<!--   tab_header( -->
<!--     title = md("**Table S2.7: Standardization of district names**")) %>% -->
<!--   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>% -->
<!--   tab_style( -->
<!--     locations = cells_column_labels(), -->
<!--     style     = list( -->
<!--       cell_text(weight = "bold")) -->
<!--   ) %>% -->
<!--   gtsave("table_s_2_7.docx") -->
<!-- ``` -->

@@

```{r table_s_2_8, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_2_8.png")

<!-- ``` {r table_standardization_district_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I") -->

<!-- district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno") -->

<!-- district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato") -->

<!-- as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>% -->
<!--   arrange(district_tobechanged) %>% -->
<!--   relocate(district_communes_affected, .before = district_tobechanged) %>% -->
<!--   rename("District name in data" = district_tobechanged, -->
<!--          "Communes" = district_communes_affected, -->
<!--          "District name, updated" = district_changed) %>% -->
<!--   gt() %>%  -->
<!--   tab_header( -->
<!--     title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>% -->
<!--   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>% -->
<!--   tab_style( -->
<!--     locations = cells_column_labels(), -->
<!--     style     = list( -->
<!--       cell_text(weight = "bold")) -->
<!--   )%>% -->
<!--   gtsave("table_s_2_8.docx") -->

\addcontentsline{lot}{table}{Table S2.9: Standardization of commune names.}

```{r table_s_2_9, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_2_9a.png")
knitr::include_graphics("table_s_2_9b.png")

<!-- ``` {r table_standardization_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord", -->
<!--                  "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana",  -->
<!--                  "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho", -->
<!--                  "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary", -->
<!--                  "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud", -->
<!--                  "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy", -->
<!--                  "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao", -->
<!--                  "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso", -->
<!--                  "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona", -->
<!--                  "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina", -->
<!--                  "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika", -->
<!--                  "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy", -->
<!--                  "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord", -->
<!--                  "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe", -->
<!--                  "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I", -->
<!--                  "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda", -->
<!--                  "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe", -->
<!--                  "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut", -->
<!--                  "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity", -->
<!--                  "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba", -->
<!--                  "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka", -->
<!--                  "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)", -->
<!--                  "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo",  -->
<!--                  "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare",  -->
<!--                  "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II", -->
<!--                  "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain", -->
<!--                  "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud", -->
<!--                  "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat", -->
<!--                  "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra", -->
<!--                  "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka") -->

<!-- commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord", -->
<!--                  "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava",  -->
<!--                  "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana", -->
<!--                  "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud", -->
<!--                  "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka", -->
<!--                  "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo", -->
